Estimated Annual Size of Claims Arising from Fire

### 2023-06-02 report/PAPER.tex
reaaaaaaaaaaaly finished

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[209050796]{easymcm}  % 载入 EasyMCM 模板文件
\problem{A}  % 请在此处填写题号
\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
%\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包

@@

% 此处填写摘要内容
\begin{abstract}
    The aim of this study is to construct a mathematical model based on Markov chains to predict \
    the total size of claims paid by insurers in the UK (and specifically England) due to fires in \
    the coming year. We split the regions of England into\ 
    \emph{"South West", "South East", "London", "East of England", "East Midlands", "Yorkshire and The Humber", "North West", "West Midlands", "North East"} \ 
    in order to obtain more refined predictions. First, we used house price data as a proxy for the \
    size of the claim per fire, assuming a fixed ratio of damage to the size of the claim per fire. \
    We then fitted the house price data with a log-normal distribution to obtain the distribution of \
    each claim size. Next, we modelled the number of fires using a Poisson distribution with a high \
    probability estimate. Finally, we use Monte Carlo simulations to estimate the size of the annual \
    fire loss. Our model takes into account two key factors, the number of fires and the size of claims \
    per fire, and provides insurers with an effective tool for predicting and managing fire insurance risk. \
    However, there are some assumptions and limitations to our model, such as our assumption of a fixed ratio \
    of losses to claim sizes per fire, which may not be entirely accurate in real life situations. \
    Future research could further improve this model to increase its predictive accuracy and usefulness. \\
    All data is taken from GOV.UK, the official website of the UK government.\\

@@

    \vspace{5pt}
    \textbf{Word Count}: 2936

@@

% \begin{subappendices}  % 附录环境

@@

% \section{Appendix B: Program Codes}
% Here are the program codes we used in our research.

@@

% % Python 代码示例
% \begin{lstlisting}[language=Python, name={test.py}]
% # Python code example
% for i in range(10):
%     print('Hello, world!')
% \end{lstlisting}

% % MATLAB 代码示例
% \begin{lstlisting}[language=MATLAB, name={test.m}]
% % MATLAB code example
% for i = 1:10
%     disp("hello, world!");
% end
% \end{lstlisting}

@@

% \end{subappendices}  % 附录内容结束

>>>>

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[209050796]{easymcm}  % 载入 EasyMCM 模板文件
\problem{A}  % 请在此处填写题号
\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
% \usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包

@@

% 此处填写摘要内容
\begin{abstract}
    The aim of this study is to construct a mathematical model to predict the total amount of claims paid by insurance companies in the UK (specifically England) due to fires in the coming year. The regions of England were divided into \emph{"South West", "South East", "London", "East of England", "East Midlands", "Yorkshire and The Humber", "North West", "West Midlands", "North East"} in order to obtain more refined predictions. Firstly, we used house price data as a proxy for the amount claimed per fire, assuming a fixed ratio of damage to the amount claimed per fire. We then fitted the house price data with a log-normal distribution to obtain the distribution of each claim amount. Next, we modelled the number of fires using a Poisson distribution with a high probability estimate. Finally, we use Monte Carlo simulations and ARIMA models to predict the amount of fire losses each year. Our model takes into account two key factors, the number of fire occurrences and the amount of claims per fire, and provides an effective tool for insurers to predict and manage fire insurance risk. However, there are some assumptions and limitations to our model, such as our assumption of a fixed ratio of losses to claim amounts per fire, which may not be entirely accurate in real life situations. Future research could further improve this model to increase its predictive accuracy and usefulness. \ 
    All data are taken from the official UK government website gov.uk\textsuperscript{\cite{fireguide,guide}}. Experiments on the house price dataset show that the model performs well in terms of accuracy and generalisability. The article also describes the mathematical notation, techniques and tools used.

@@

@@

\begin{subappendices}  % 附录环境

@@

\section{Appendix A: Program Codes}
% Here are the program codes we used in our research.

@@

% Python 代码示例
\begin{lstlisting}[language=Python, name={simulate_fire_ratio}]
def simulate_fire_ratio(poisson_all, 
                        poisson_residential, 
                        num_simulations=1000000):
    # Calculate the probability of a fire occurring in a residence once
    p = poisson_residential.args[0] / poisson_all.args[0]

    # Draw the number of all fires from the Poisson distribution
    all_fires = poisson_all.rvs(num_simulations)

    # Simulate the number of all fires per year to determine 
    # how many are residential fires
    residential_fires = np.random.binomial(all_fires, p)

    # To prevent a division by 0 error, 
    all_fires[all_fires == 0] = 1

    # Calculate the ratios
    ratios = residential_fires / all_fires

    # Return the array of ratios
    return ratios
\end{lstlisting}

\begin{lstlisting}[language=Python, name={calculate_S_pdf}]
    def calculate_S_pdf(norm_dist, 
    poisson_dist, 
    offset_cliam, 
    offset_fire_times, 
    n_bins=1000):
    # Generate possible values of S.

    # Determine the maximum possible value of N 
    # based on the quantile of the Poisson distribution    
    max_n = int(poisson_dist.ppf(0.999))

    # Range of N values
    N_values = np.arange(0-offset_fire_times, max_n-offset_fire_times)  
    # Range of X values
    X_values = np.linspace(norm_dist.ppf(0.001)-offset_cliam, 
                           norm_dist.ppf(0.999)-offset_cliam, 
                           n_bins)

    # Calculate the probability for each S value.

    # Probability of N
    N_probs = poisson_dist.pmf(N_values+offset_fire_times)  
    # Probability of X
    X_probs = norm_dist.pdf(X_values+offset_cliam)  
    # Probability of all possible S values
    S_probs = np.outer(N_probs, X_probs)

    # Calculate the probability density function of S
    S_pdf = np.sum(S_probs, axis=0)

    return X_values, S_pdf
\end{lstlisting}

\begin{lstlisting}[language=Python, name={predict_house_price_mean}]
    def predict_house_price_mean(r):

        def create_ARMA_model(data, order=(2, 3, 0)):
            # Convert data to time series
            ts = pd.Series(data)
            ts.index = pd.Index(pd.date_range('2011', 
                                            periods=len(data), 
                                            freq='Y'))

            # fit model
            model = ARIMA(ts, order=order)
            model_fit = model.fit()

            return model_fit

        house_price = []

        for y in all_year:
            house_price.append(np.mean(np.log(
                search_region_and_year_house_prices(r, y)
                )))

        model = create_ARMA_model(house_price)
        prediction = model.predict(start=len(house_price), 
                                   end=len(house_price)+1)
    return prediction
\end{lstlisting}
% % MATLAB 代码示例
% \begin{lstlisting}[language=MATLAB, name={test.m}]
% % MATLAB code example
% for i = 1:10
%     disp("hello, world!");
% end
% \end{lstlisting}

@@

\end{subappendices}  % 附录内容结束
